\vskip-0.6in \Large Political Uncertainty

### 2016-02-20 two-groups.tex
fix mistake in FOCs for 2NNBs case

\newpage
\section{Math for Discrete Model}
The math that follows from Equation \ref{eq:logistic}:
\begin{itemize}
	\item Then Equation \ref{eq:logistic} is equivalent to:
		\begin{equation}
			\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z} }
					\label{eq:logistic2}
		\end{equation}
		\[
			\frac{2 + e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\[
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\begin{equation}
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Likewise, we have
		\begin{equation}
			\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
		\end{equation}
		and
		\begin{equation}
			\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
			\label{eq:base}
		\end{equation}
		Setting the left-hand size of these last two equations (the FOCs for the bribes for 0 and $\frac{1}{2}$ equal to each other,
		\[
		  \frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}
		\]
		\[
		  \frac{e^{-X-Y} + e^{-X-Z}}{1+e^{-X}}= \frac{e^{-X-Y} + e^{-Y-Z}}{1+e^{-Y}}
		\]
		\[
		  e^{-X-Y} + e^{-X-Z} + e^{-X-2Y} +e^{-X-Y-Z}= e^{-X-Y} + e^{-Y-Z} + e^{-2X-Y} +e^{-X-Y-Z}
		\]
		\[
		  e^{-X-Z} +e^{-X-2Y}= e^{-Y-Z} +e^{-2X-Y}
		\]
		\[
		  e^{-Z} +e^{-2Y}= e^{X-Y-Z} +e^{-X-Y}
		\]
		\begin{equation}
		  e^{Y-Z} +e^{-Y}= e^{X-Z} +e^{-X}
			\label{eq:twoways}
		\end{equation}
   Equation~\ref{eq:twoways} can be rearranged into two similar forms. First:
		\[
		  e^{Y-Z} - e^{X-Z}= e^{-X} - e^{-Y}
		\]
		\begin{equation}
		  e^{Y} - e^{X}= e^Z\left(e^{-X} - e^{-Y}\right)
			\label{eq:1}
		\end{equation}
  	Second, multiplying through by zero:
	  \begin{equation}
		  e^{X} - e^{Y}= e^Z\left(e^{-Y} - e^{-X}\right)
			\label{eq:2}
		\end{equation}
	\end{itemize}	
In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b\left(\frac{1}{2}\right)$, we know that $Z < 0$ (not true because we can have $\alpha < -.5$). Note that this is due to the construction of the problem. This means $e^Z < 1$. In this case,
	\begin{itemize}
		\item Equation~\ref{eq:1} is consistent with $X>Y>0$, $X>0>Y$, or $0>X>Y$.
		\item Equation~\ref{eq:2} is consistent with $Y>X>0$, $Y>0>X$, or $0>Y>X$.
	\end{itemize}
The second order conditions will pin down the solution in this case of two non-negative bribes.

\begin{itemize}
	\item SOCs imply that both $X$ and $Y$ are positive.
\end{itemize}

>>>>

\newpage
\section{Math for Discrete Model}
The math that follows from Equation \ref{eq:logistic}:
\begin{itemize}
	\item Then Equation \ref{eq:logistic} is equivalent to:
		\begin{equation}
			\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z} }
					\label{eq:logistic2}
		\end{equation}
		\[
			\frac{2 + e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\[
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\begin{equation}
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Likewise, we have
		\begin{equation}
			\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
		\end{equation}
		and
		\begin{equation}
			\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
			\label{eq:base}
		\end{equation}
		Setting the left-hand size of these last two equations (the FOCs for the bribes for 0 and $\frac{1}{2}$ equal to each other,
		\[
		  \frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}
		\]
		\[
		  \frac{e^{-X-Y} + e^{-X-Z}}{1+e^{-X}}= \frac{e^{-X-Y} + e^{-Y-Z}}{1+e^{-Y}}
		\]
		\[
		  e^{-X-Y} + e^{-X-Z} + e^{-X-2Y} +e^{-X-Y-Z}= e^{-X-Y} + e^{-Y-Z} + e^{-2X-Y} +e^{-X-Y-Z}
		\]
		\[
		  e^{-X-Z} +e^{-X-2Y}= e^{-Y-Z} +e^{-2X-Y}
		\]
		\[
		  e^{-Z} +e^{-2Y}= e^{X-Y-Z} +e^{-X-Y}
		\]
		\begin{equation}
		  e^{Y-Z} +e^{-Y}= e^{X-Z} +e^{-X}
			\label{eq:twoways}
		\end{equation}
   Equation~\ref{eq:twoways} can be rearranged into two similar forms. First:
		\[
		  e^{Y-Z} - e^{X-Z}= e^{-X} - e^{-Y}
		\]
		\begin{equation}
		  e^{Y} - e^{X}= e^Z\left(e^{-X} - e^{-Y}\right)
			\label{eq:1}
		\end{equation}
  	Second, multiplying through by zero:
	  \begin{equation}
		  e^{X} - e^{Y}= e^Z\left(e^{-Y} - e^{-X}\right)
			\label{eq:2}
		\end{equation}
	\end{itemize}	
In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b\left(\frac{1}{2}\right)$, there are two possibilities. If $Z < 0$, $e^Z < 1$. In this case,
	\begin{itemize}
		\item Equation~\ref{eq:1} is consistent with $X\geq Y\geq 0$, $X\geq 0 \geq Y$, or $0 \geq X \geq Y$.
		\item Equation~\ref{eq:2} is consistent with $Y \geq X \geq 0$, $Y \geq 0 \geq X$, or $0 \geq Y \geq X$.
	\end{itemize}

If $Z > 0$, $e^Z < 1$. In this case, ...

The second order conditions will pin down the solution in this case of two non-negative bribes.

\begin{itemize}
	\item SOCs imply that $X$ and $Y$ are either both positive, both negative, or one zero and the other unrestricted. But we can use these inequalities to get rid of the last case [finish this]
\end{itemize}
